### 2020-03-04 model.tex
expanding modeling approach chapter

Serpent 2 \cite{leppanen_serpent_2014} is a continuous-energy Monte Carlo
reactor physics code under
active development at the VTT Technical Research Centre of Finland. It was
born in 2004 out of the need for better general-purpose neutron transport
codes for group constant generation in lattice geometries, and has since grown
to support more general capabilities, for an active user base of more than 500
people worldwide. Serpent is highly parallelizable due to its support for
both MPI and OpenMP parallel programming APIs, and highly validated and
verified against experimental data and other well-established codes.

@@

In the context of this project, we used Serpent with the JEFF-3.1.2 nuclear
data library \cite{oecd/nea_jeff-3.1.2_2014} to generate group constants
for Moltres. The reactor geometry is based on the axisymmetric \gls{MSFR}
neutronics benchmark geometry published in several previous papers involving
the \gls{MSFR}. The relevant group constant data are collapsed into six
neutron energy groups, and calculated for
temperature values of 900 K to 1200 K at 50 K intervals.

@@

Moltres is a \gls{MOOSE}-based application for coupled
neutronics/thermal-hydraulics simulations of \glspl{MSR}. \gls{MOOSE} is a
highly parallelizable,
finite-element framework developed at \gls{INL} for simplifying the process of
creating fully-coupled, non-linear, multiphysics solvers. The framework
provides a user-friendly interface for this task through object-oriented
programming in C++. All aspects of a typical multiphysics problem, such as the
terms in the \glspl{PDE}, the initial and boundary conditions, the material
properties, etc., are represented in \gls{MOOSE} as C++ objects. This approach
is helpful for many researchers, a significant fraction of whom do not possess
high-level programming backgrounds, as they are unencumbered by the
technical details and complexicities involved in programming mesh handling
and \gls{PDE} solving in finite element analysis.

\gls{MOOSE} itself relies heavily on LibMesh and PETSc for
its mesh handling and \gls{PDE} solver functionalities. As a result,
\gls{MOOSE} supports adaptive meshing schemes and automatic variable scaling
amongst other features for improved accuracy and performance times. Full
coupling is maintained by the execution of Newton-based solves on the
weak formulations of the multiple \glspl{PDE} to minimize the residual values.
Fully-coupled solves are essential for accurately resolving systems with
strongly interacting physics. The \gls{MSR} concept is one such example, where
the neutronics and thermal-hydraulics are tightly coupled through the Doppler
effect and the temperature dependence of liquid fuel salt density.

\gls{MOOSE}, and Moltres by extension, are capable of up to 3D geometry
modelling. They support a wide range of input mesh file formats listed in a
\gls{MOOSE} webpage, including the commonly used Exodus II file format.
Specifically for the 2D case, axial symmetry is easily imposed by changing
one line of code in the input file, without any changes in the Cartesian
representations of the \glspl{PDE} and boundary conditions in their original
C++ implementations. This feature provides significant computational time
savings for 3D systems that exhibit high axial symmetry. Another important
feature for reducing computational time is the use of MPI for parallel
computing. All \gls{MOOSE}-based codes can be easily compiled and run on high
performance computing clusters.

@@

Focusing our attention on Moltres, the neutron flux calculations are
performed using the standard formulations for the time-dependent multi-group
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
	\frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
	\nabla \phi_g - \Sigma^r_g \phi_g
	\sum^G_{g \neq g'} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
	\sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
	\lambda_i C_i, \label{eq:neut} \\
	\frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
	\phi_{g'} - \lambda_i C_i - \boldsymbol{u} \cdot \nabla C_i + \nabla \cdot
	\frac{\mu_t}{\rho Sc_t} \nabla C_i, \label{eq:dnp} \\
	\intertext{where} v_g &= \text{average speed of neutrons in group }g 
	\nonumber \\
	\phi_g &= \text{flux of neutrons in group }g \nonumber \\
	t &= \text{time} \nonumber \\
	D_g &= \text{diffusion coefficient of neutrons in group }g \nonumber \\
	\Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons from
	group }g \nonumber \\
	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
	scattering from }g' \text{ to }g \nonumber \\
	\chi^p_g &= \text{prompt fission spectrum neutrons in group }g \nonumber
	\\
	G &= \text{total number of discrete neutron groups} \nonumber \\
	\nu &= \text{average number of neutrons produced per fission} \nonumber \\
	\Sigma^f_{g} &= \text{macroscopic fission cross-section for neutron in
	group }g \nonumber \\
	\chi^d_g &= \text{delayed fission spectrum neutrons in group }g \nonumber
	\\
	I &= \text{total number of delayed neutron precursor groups} \nonumber \\
	\beta &= \text{total delayed neutron fraction} \nonumber \\
	\beta_i &= \text{delayed neutron fraction of precursor group i} \nonumber
	\\
	\lambda_i &= \text{average decay constant of delayed neutron precursors in
	precursor group }i \nonumber \\
	C_i &= \text{concentration of delayed neutron precursors in precursor
	group }i \nonumber
\end{align}
%

The limitations of the multi-group neutron diffusion compared to
S$_{\text{N}}$ and Monte Carlo methods are well-documented but they provide
decent accuracy at lower computational costs. A comparison of the
multiplication factor and reactivity coefficients in the context of the
\gls{MSFR} is provided in the results section.

The \gls{DNP} concentration equation has an additional advection term to
account for the movement of \glspl{DNP} in the primary coolant loop. Moltres
also accounts for the decay of \glspl{DNP} outside the active core
region by simulating its flow in a separate 1D geometry. The length and
velocity defined in this geometry may differ according to reactor
specifications.

Moltres users may call for an arbitrary number of neutron energy groups as
long as they provide Moltres with the appropriate group constant data. The
number of precursor groups is also arbitrary, though usually pre-determined by
the choice of nuclear data library in the group constant generation step.
Moltres automatically interpolates the group constant data for required
temperatures using one of the many pre-defined interpolation methods available
in \gls{MOOSE}. Once again, users have the freedom to select their
interpolation method of choice. For this work, we have selected six neutron
energy groups according to the energy boundaries in table \ref{table:bound},
eight \gls{DNP} groups as defined by the JEFF-3.1.2 library, and the spline
interpolation method.
%
\begin{table}[htb!]
	\centering
	\caption{Neutron energy group upper bounds used in Serpent.}
	\begin{tabular}{c S}
		\hline
		{Group number} & {Upper bound [MeV]}\\
		\hline
		1 & 20\\
		2 & 2.2313\\
		3 & 0.4979\\
		4 & 2.47875$\times 10^{-2}$\\
		5 & 5.5308$\times 10^{-3}$\\
		6 & 7.485$\times 10^{-4}$\\
		\hline
	\end{tabular}
	\label{table:bound}
\end{table}

For the decay heat model, previous studies on the MSFR * have shown that
using three decay heat precursor groups with different half-lives can model
decay heat in the MSFR for up to 300 seconds after shutdown with a relative
error of less than 2 \%. Thus, we implemented the decay heat model using
equations similar to the \gls{DNP} equations, as shown in eq
\ref{eq:decayheat}:
%
\begin{align}
	\frac{\partial D^k}{\partial t} &= f_k \sum^G_{g'=1} \epsilon_{g'}
	\Sigma^f_{g'} \phi_{g'} - \lambda^k D^k - \boldsymbol{u} \cdot \nabla D^k
	+ \nabla \cdot \frac{\mu_t}{\rho Sc_t} \nabla D^k, \label{eq:decayheat} \\
	\intertext{where}
	D^k &= \text{concentration of decay heat precursors in group }k \nonumber
	\\
	f_k &= \text{fraction of decay heat to total power at steady state}
	\nonumber \\
	\epsilon_g &= \text{average fission energy} \nonumber \\
	\lambda^k &= \text{average decay constant of decay heat precursors in
	group }k. \nonumber
\end{align}

@@

The governing equation for temperature in the molten salt is given as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} &= - \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) + Q_s - Q_{hx},
	\label{eq3}
	\intertext{where}
	\rho &= \text{density of molten salt} \nonumber \\
	c_{p} &= \text{specific heat capacity of molten salt} \nonumber \\
	T &= \text{temperature of molten salt} \nonumber \\
	\overrightarrow{u} &= \text{velocity of molten salt} \nonumber \\
	k &= \text{thermal conductivity of molten salt} \nonumber \\
	Q_{hx} &= \text{heat sink},
\end{align}
	and the source term $Q_s$ is given as:
%
\begin{align}
Q_s = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}

In the \gls{MSFR}, salt flow in the core has a Reynolds number on the order of
10$^6$*. Thus the Navier-Stokes module in \gls{MOOSE} cannot sufficiently
capture the turbulent flow behavior. Furthermore, the \gls{MSFR} benchmark
geometry encourages the formation of turbulent recirculation regions in the
fuel salt near the blanket tank regions. Due to this present limitation, only
the flow in the active core region is simulated and it is assumed to be
vertical flow. This eliminates the presence of recirculation zones reported by
*, which will likely be a source of discrepancy between our results and
theirs. Another consequence is the absence of turbulent diffusion, resulting
in higher-than-expected temperatures along the central axis of the reactor
where the neutron flux and heat generation is highest. This is further
exacebated by the high Prandtl number of the molten salt; heat transfer is
dominated by convective flow. This means that there would be very low heat
transfer observed by diffusion due to the negligible contributions from
heat conduction.

>>>>

Serpent 2 \cite{leppanen_serpent_2014} is a continuous-energy Monte Carlo
reactor physics code under
active development at the VTT Technical Research Centre of Finland. It was
created in 2004 out of the need for better general-purpose neutron transport
codes for group constant generation in lattice geometries, and has since grown
to support more general capabilities, for an active user base of more than 500
people worldwide. Serpent is highly parallelizable due to its support for
both MPI and OpenMP parallel programming APIs, and highly validated and
verified against experimental data and other well-established codes.

@@

In the context of this project, we used Serpent with the JEFF-3.1.2 nuclear
data library \cite{oecd/nea_jeff-3.1.2_2014} to generate group constants
for Moltres. The reactor geometry is based on the axisymmetric \gls{MSFR}
neutronics benchmark geometry published in several previous papers involving
the \gls{MSFR}, as shown in Fig. \ref{fig:msfrgeom}. The relevant group
constant data are collapsed into six neutron energy groups, and calculated for
temperature values of 800 K to 1300 K at 50 K intervals.

@@

Moltres is a \gls{MOOSE}-based application for coupled
neutronics/thermal-hydraulics simulations of \glspl{MSR}. \gls{MOOSE}
\cite{gaston_physics-based_2015} is a highly parallelizable,
finite-element framework developed at \gls{INL} for simplifying the process of
creating fully-coupled, non-linear, multiphysics solvers. The framework
provides a user-friendly interface for this task through object-oriented
programming in C++. All aspects of a typical multiphysics problem, such as the
terms in the \glspl{PDE}, the initial and boundary conditions, the material
properties, etc., are represented in \gls{MOOSE} as C++ objects. New objects
can inherit properties from related old objects to simplify implementation and
reduce code duplication. Overall, this approach
is helpful for many researchers, a significant fraction of whom do not possess
high-level programming backgrounds, as they are unencumbered by the
technical details and complexicities involved in programing mesh handling
and \gls{PDE} solving in finite element analysis.

\gls{MOOSE} itself relies heavily on libMesh \cite{kirk_libmesh:_2006} and
PETSc \cite{satish_petsc_2019} for its mesh handling and \gls{PDE} solver
functionalities. As a result, \gls{MOOSE} supports adaptive meshing schemes
and automatic variable scaling amongst other advanced features for improved
accuracy and performance times. Full
coupling is maintained by the execution of Newton-based solves on the
weak formulations of the multiple \glspl{PDE} to minimize the residual values.
Fully-coupled solves are essential for accurately resolving systems with
strongly interacting physics. The \gls{MSR} concept is one such example, where
the neutronics and thermal-hydraulics are tightly coupled through the Doppler
effect and the temperature dependence of liquid fuel salt density.

\gls{MOOSE}, and Moltres by extension, are capable of up to 3D geometry
modelling. They support a wide range of input mesh file formats listed in a
\gls{MOOSE} webpage, including the commonly used Exodus II file format.
Specifically for the 2D case, axial symmetry is easily and automatically
imposed by changing one line of code in the input file, without any changes in
the Cartesian representations of the \glspl{PDE} and boundary conditions in
their original C++ implementations. This feature provides significant
computational time savings for 3D systems that exhibit high axial symmetry.
Another important feature for reducing computational time is the use of MPI
for parallel computing. All \gls{MOOSE}-based codes can be compiled and
run on high performance computing clusters.

@@

Focusing our attention on Moltres, the neutron flux calculations are
performed using the standard formulations for the time-dependent multi-group
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \boldsymbol{u} \cdot \nabla C_i + \nabla \cdot
    D_t \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm s$^{-1}$]} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}$ s$^{-1}$]} \nonumber
    \\
    t &= \text{time [s]} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$ [cm$^2$
    s$^{-1}$]} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons from
    group $g$ [cm$^{-1}$]} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
    scattering from $g'$ to $g$ [cm$^{-1}$]} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$}
    \nonumber \\
    G &= \text{total number of discrete neutron groups} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission} \nonumber \\
    \Sigma^f_{g} &= \text{macroscopic fission cross-section for neutron in
    group $g$ [cm$^{-1}$]} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group }g
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups} \nonumber \\
    \beta &= \text{total delayed neutron fraction} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$} \nonumber \\
    D_t &= \text{turbulent diffusion of the delayed neutron precursors [cm$^2$
    s$^{-1}$]} \nonumber
\end{align}
%

While the limitations of the multi-group neutron diffusion compared to other
deterministic and Monte Carlo methods, particularly for flux values near
boundaries, are well-documented, it provides acceptable
accuracy at lower computational costs. Moreover, the
\gls{MSFR} contains no material interfaces in the middle of the core where
most of the fission interactions take place. The results section provides a
comparison of the \gls{MSFR} multiplication factor values and reactivity
coefficients between Moltres and Serpent.

The \gls{DNP} concentration equation has additional advection and turbulent
diffusion terms to account for the movement of \glspl{DNP} in the primary
coolant loop. The turbulent diffusion value is governed by the following
equation:
%
\begin{align}
    D_t &= \frac{\mu_t}{\rho Sc_t}
\end{align}
%
where $\mu_t$ is the eddy viscosity [kg cm$^{-1}$ s$^{-1}$] , $\rho$ is the
density of the fuel salt [kg cm$^{-3}$], and $Sc_t$ is the turbulent Schmidt
number. We assumed $Sc_t = 0.85$ for a fair comparison with the Polimi/TUDelft
models which used the same value. Moltres also accounts for the decay of
\glspl{DNP} outside the active core region by simulating its flow in a
separate 1D pipe geometry. This outer loop pipe simulation is loosely coupled
to the active core simulation through MOOSE's MultiApp functionality and
inlet/outlet boundary values. The loose coupling is justified as the evolution
of \gls{DNP} concentrations due to inflow is relatively slow. The length and
velocity defined in this geometry may differ according to reactor
specifications. For this work with the \gls{MSFR} model, we assumed a pipe
length of 2.255 m with salt flowing at 1.1275 m s$^{-1}$ for an out-of-core
residence time of 2 seconds to follow the design specifications.

Moltres users may vary the total number of neutron energy groups as
long as they provide Moltres with the appropriate group constant data. The
number of precursor groups is also variable, though usually pre-determined by
the choice of nuclear data library in the group constant generation step.
Moltres automatically interpolates the group constant data for required
temperatures using one of the many pre-defined interpolation methods available
in \gls{MOOSE}. Once again, users have the freedom to select their
interpolation method of choice.

For this work, we have six neutron energy groups according to the energy
boundaries in table \ref{table:bound}, eight \gls{DNP} groups as defined by
the JEFF-3.1.2 library, and the spline interpolation method. The neutron flux
and \gls{DNP} concentration values were approximated by first-order Lagrange
and constant monomial shape functions respectively on the finite element mesh.
We assumed vacuum boundary conditions for all six neutron group fluxes along
the external boundaries of the geometry, and homogeneous Neumann boundary
conditions along the axial symmetry boundary. For the \gls{DNP}
concentrations, we imposed homogeneous Neumann boundary conditions on the
walls, and inflow and outflow boundary conditions on the inlet and outlet
boundaries respectively. The inlet \gls{DNP} concentration values were
imported from the outlet values of the 1-D outer loop pipe at the same
timestep.

\begin{table}[htb!]
	\centering
	\caption{Neutron energy group upper bounds used in Serpent.}
	\begin{tabular}{c S}
		\toprule
		{Group number} & {Upper bound [MeV]}\\
		\midrule
		1 & 20\\
		2 & 2.2313\\
		3 & 0.4979\\
		4 & 0.0247875\\
		5 & 0.0055308\\
		6 & 0.0007485\\
		\bottomrule
	\end{tabular}
	\label{table:bound}
\end{table}

For the decay heat model, a previous study on the MSFR by Aufiero et al.
\cite{aufiero_extended_2013} has shown that using three decay heat precursor
groups with different half-lives in the form of exponential equations, can
accurately model decay heat in the MSFR for up to 300 seconds after shutdown
with a relative error of less than 2 \%. Thus, we implemented a decay heat
model using the following set of equations:
%
\begin{align}
	\frac{\partial \omega_k}{\partial t} &= f_k \sum^G_{g=1} \epsilon_{g}
	\Sigma^f_{g} \phi_{g} - \lambda^k \omega_k - \boldsymbol{u} \cdot \nabla
	\omega_k + \nabla \cdot D_t \nabla \omega_k, \label{eq:decayheat} \\
	\intertext{where}
    \omega_k &= \text{total decay heat power density from decay heat
    precursors in group $k$ [W cm$^{-3}$]} \nonumber \\
	f_k &= \text{fraction of decay heat to total power at steady state}
	\nonumber \\
	\epsilon_g &= \text{average fission energy per fission [W]} \nonumber \\
	\lambda^k &= \text{average decay constant of decay heat precursors in
	group $k$ [s$^{-1}$].} \nonumber
\end{align}

Like the neutron and \gls{DNP} groups, Moltres can take an arbitrary number of
decay heat groups. In this work, as with the other parameters, we used the
same decay heat fractions and decay constants used in the Polimi/TUDelft
models for three decay heat groups.

\begin{table}[htb!]
	\centering
	\caption{Decay heat group parameters \cite{fiorina_modelling_2014}.
	$\lambda_i$ and $f_i$ are the decay constants and decay heat fractions
	associated to group $i$.}
	\begin{tabular}{S S S}
		\toprule
		{Decay heat group} & {$\lambda_i$ [s$^{-1}$]} & {$f_i$} \\
		\midrule
		1 & 0.1974 & 0.0117 \\
		2 & 0.0168 & 0.0129 \\
		3 & 3.58 $\times 10^{-4}$ & 0.0186 \\
		\bottomrule
	\end{tabular}
	\label{table:decayheat}
\end{table}

@@

The governing equation for temperature in the molten salt is:
%
\begin{align}
    \rho c_{p} \frac{\partial T}{\partial t} &= - \rho c_p \boldsymbol{u}
    \cdot \nabla T + \nabla \cdot k \nabla T + Q_s - Q_{hx},
    \label{eq:th}
    \intertext{where}
    \rho &= \text{density of molten salt} \nonumber \\
    c_{p} &= \text{specific heat capacity of molten salt} \nonumber \\
    T &= \text{temperature of molten salt} \nonumber \\
    \overrightarrow{u} &= \text{velocity of molten salt} \nonumber \\
    k &= \text{thermal conductivity of molten salt} \nonumber \\
    Q_{hx} &= \text{heat sink},
\end{align}
	and the source term $Q_s$ is:
%
\begin{align}
    Q_s = \Big( 1 - \sum^K_{k=1} f_k \Big) \sum^G_{g=1} \epsilon_g \Sigma_g^f
    \phi_g + \sum^K_{k=1} \omega_k, \label{eq:source}
\end{align}
%
where $K$ is the total number of decay heat groups.

Salt flow in the core is governed by the standard incompressible Navier-Stokes
equations:
%
\begin{align}
    \rho \frac{\partial \boldsymbol{u}}{\partial t} &= -\rho (\boldsymbol{u}
    \cdot \nabla) \boldsymbol{u} + \nabla \cdot (-p \boldsymbol{I} + \mu [
    \nabla \boldsymbol{u} + (\nabla \boldsymbol{u})^T] + \boldsymbol{f}
    \label{eq:momemtum} \\
    \nabla \cdot \boldsymbol{u} &= 0 \label{eq:divergence}
    \intertext{where}
    p &= \text{ pressure} \nonumber \\
    \mu &= \text{ dynamic viscosity} \nonumber \\
    \boldsymbol{f} &= \text{ body force per unit volume} \nonumber
\end{align}

In the \gls{MSFR}, salt flow in the core has a Reynolds number on the order of
10$^6$. Thus the Navier-Stokes module in \gls{MOOSE} cannot sufficiently
capture the turbulent flow behavior. Furthermore, the \gls{MSFR} benchmark
geometry encourages the formation of turbulent recirculation regions in the
fuel salt near the blanket tank regions as seen in the Polimi/TUDelft models
\cite{fiorina_modelling_2014}. Moltres does not have a turbulence model in its
current implementation. Therefore, instead of solving for the eddy viscosity
with a two-equation \gls{RANS} model, we took a zeroth-order approximation of
the eddy viscosity based on results reported by Fiorina et al.
\cite{fiorina_modelling_2014}. We assumed $\mu_t = 40$ Pa s throughout the
core.

Another consequence is the absence of turbulent diffusion, resulting
in higher-than-expected temperatures along the central axis of the reactor
where the neutron flux and heat generation is highest. This is further
exacebated by the high Prandtl number of the molten salt; heat transfer is
dominated by convective flow. This means that there would be very low heat
transfer observed by diffusion due to the negligible contributions from
heat conduction.

### 2020-03-04 msfr.tex
expanding modeling approach chapter

For this work, we used a model similar to the reference square-cylindrical
\gls{MSFR} design to benchmark our results against results published by
Fiorina et al. and Aufiero et al. The reference design is a 2-D axisymmetric
model with the sixteen individual external loops homogenized into a single
outer loop as shown in Fig. \ref{fig:msfrgeom}. For the multi-group
cross sections and group constants calculations in Serpent, we extended this
2-D axisymmetric model into a 3-D model by a simple full rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model. Accordingly, the pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this may not be entirely
accurate, the exact details of the pump and heat exchanger systems are still
be researched, and this external loop region is presumed to be of little
neutronic importance due to its position behind the strong boron carbide
neutron absorber layer.
%
\begin{figure}[htb!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent and Moltres. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

@@

As mentioned before, the fuel and blanket salts are comprised of a 77.5\% LiF
- 22.5\% AcF$_4$ mixture. This is the reference salt composition of the
\gls{MSFR} at start-up. Typically, researchers working with the \gls{MSFR}
model calculate the exact actinide composition by varying the $^{232}$Th to
$^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a uniform
temperature of 973 K. Thus, the exact actinide compositions vary depending on
the nuclear data library and neutron transport code. The exact composition
used for this work can be found in the Results chapter. We assume that the
effects of these composition variations on the reference physical properties
of the fuel and blanket salt are negligible. Table \ref{table:prip} shows
relevant physical properties of the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$.}
\begin{tabular}{l l r r}
\toprule
Property & Expression & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Boiling temperature [K] & 1874 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $1.015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $0.01010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1555$* & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}

>>>>

For this work, we used a model similar to the reference square-cylindrical
\gls{MSFR} design to benchmark our results against results published by
Fiorina et al. and Aufiero et al. The reference design is a 2-D axisymmetric
model with the sixteen individual external loops homogenized into a single
outer loop as shown in Fig. \ref{fig:msfrgeom}. For the multi-group
cross sections and group constants calculations in Serpent, we extended this
2-D axisymmetric model into a 3-D model by a simple full rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model. Accordingly, the pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this may not be entirely
accurate, the exact details of the pump and heat exchanger systems are still
be researched, and this external loop region is presumed to be of little
neutronic importance due to its position behind the strong boron carbide
neutron absorber layer.
%
\begin{figure}[htb!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

@@

As mentioned before, the fuel and blanket salts are comprised of a 77.5\% LiF
- 22.5\% AcF$_4$ mixture. This is the reference salt composition of the
\gls{MSFR} at start-up. Typically, researchers working with the \gls{MSFR}
model calculate the exact actinide composition by varying the $^{232}$Th to
$^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a uniform
temperature of 973 K. Thus, the exact actinide compositions vary depending on
the nuclear data library and neutron transport code. The exact composition
used for this work can be found in the Results chapter. We assume that the
effects of these composition variations on the reference physical properties
of the fuel and blanket salt are negligible. Table \ref{table:prip} shows
relevant physical properties of the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Boiling temperature [K] & 1874 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $1.015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $0.01010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1555$* & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}
